---
title: "Assignment 1"
author: "Trinh Nhat Minh Le"
format: html
editor: visual
---

# 1. Git and GitHub

URL to my assignment's directory on GitHub: <https://github.com/minhclone4641/econ_3201>.

# 2. Latex

#### Rewrite mentioned equations in Latex

(a)Â $E(Y) = y_1p_1 + ... + y_kp_k = \sum_{i=1}^ky_ip_i$.

(b)Â $\sigma_Y = Var(Y) = E[(Y - \mu_y)^2] = \sum_{i=1}^k(y_i-\mu_y)^2p_i$

(c)Â $\hat{\beta} = \frac{\sum_{i=1}^n(y-y_i)(x-x_i)}{\sum_{i=1}^n(x-x_i)^2}$

(d)Â $P(a \leq Y \leq b) = \int_{a}^{b}f_Y(y)dy$

(e)Â $\hat{g}(x) = \frac
{\frac{1}{nh}\sum_{i=1}^n y_ik(\frac{x_i-x}{h})}
{\frac{1}{nh}\sum_{i=1}^n k(\frac{x_i-x}{h})}$

# 3. R

### 3.1 Assignment

#### (a) Set the sample size

```{r}
n <- 1000
```

#### (b) Generate 2 random variables $u_1$ and $u_2$

#### With n/2 = 500 observations, \~U(0,1)

```{r}
u1 <- runif(n/2,0,1) 
u2 <- runif(n/2,0,1)

```

#### (c) Generate z1 and z2

```{r}
z1 <- sqrt(-2*log(u1))*cos(2*pi*u2)
z2 <- sqrt(-2*log(u1))*sin(2*pi*u2)
```

#### (d) Generate a vector z =\[z1,z2\]

```{r}
z <- c(z1,z2)
```

#### (e) Generate two variables $\mu$ and $\sigma$. set $\mu = 5$ and $\sigma =2$

```{r}
mu <- 5
sigma <- 2
```

#### (f) Generate a varieble $x = \mu + \sigma x z$

```{r}
x <- mu + sigma * z
```

#### (g) Calculate the mean and standard deviation of x

```{r}
mean(x)
sd(x)
```
#### Plot a histogram of ð‘¥ with the normal distribution curve

```{r}
hist(x,
freq = FALSE,
ylab = "Density",
xlab = "$x$")
curve(dnorm(x, mean = mu, sd = sigma),
col = "red", lwd = 2, add = TRUE)
```

### 3.2 Data frames and Indexing